### 2019-01-03 tex/paper.tex
Incorporated Chris's suggestions.

\mysection{Introduction}
The desirable optimization properties of submodular set functions have been
widely exploited in the design of approximate MAP estimation algorithms for
discrete conditional random fields (CRFs) \citep{boykov2001fast,
kumar2011improved}. Submodularity has also been recently used to design an
elegant variational inference algorithm to compute the marginals of a discrete
CRF by minimising an upper-bound on the log-partition function. In the initial
work of \citep{djolonga2014map}, the energy of the CRF was restricted to be submodular. In a later work ~\citep{zhang2015higher}, the algorithm was extended to handle more general Potts energy functions. The key idea here is to define a large ground set such that its subsets represent valid labelings, sublabelings or even incorrect labelings (these may assign two separate labels to a random variable and hence be invalid). Given the large ground set, it is possible to define a submodular set function whose value is equal to the energy of the CRF for subsets that specify a valid labeling of the model. We refer to such a set function as a {\em submodular extension} of the energy.

@@

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. Specifically, the Lovasz extension of a submodular extension can be shown to be an objective function for the LP relaxation. This
connection has four important practical consequences. First, it establishes
the optimality of the submodular extension of the Potts model, via the tightest LP relaxation
under UGC-hardness assumptions. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Fourth, we obtain an accurate 
submodular extension for a higher-order diversity model based on an LP
relaxation. Higher-order models can capture interesting properties of the image that cannot be
done using pairwise models~\citep{vineet2014filter, kohli2007p3}. We show that our upper-bounds on synthetic problems are comparable to those from tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using pairwise dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. We also perform semantic segmentation on the MSRC-21 dataset using a combination of dense pairwise and higher-order diversity model. The complete code is available at \url{https://github.com/pankajpansari/denseCRF}.

@@

We now introduce the notation and definitions that we will make use of in the remainder of the paper.

@@

\myparagraph{Lovasz Extension} For a given set function $F$ with $F(\emptyset) = 0$, the value of its Lovasz extension $f({\bf w}): \mathbb{R}^N \to \mathbb{R}$ is defined as follows: order the components of $\bf w$ in decreasing order such that $w_{j_1} \geq w_{j_2} \geq \dots \geq w_{j_N}$, where $(j_1, j_2, \dots, j_N)$ is the corresponding permutation of the indices. Then,
%
\begin{align}
    f({\bf w}) = \sum_{k = 1}^{N} w_{j_k} \left(F(j_1, \dots, j_k) - F(j_1,
    \dots, j_{k - 1})\right).
    \label{eq:lovasz_def}
\end{align}
%
The function $f$ is an extension because it equals $F$ on the vertices of the
unit cube. That is, for any $A \subseteq V$, $f({\bf 1}_A) = F(A)$ where ${\bf
1}_A$ is the $0\mhyphen{1}$ indicator vector corresponding to the elements of $A$.

@@

We can augment the above pairwise models with higher-order potentials. Let $\mathcal C$ be the set of cliques, that is, fully-connected groups of variables. These cliques can, for instance, be the set of superpixels from an image segmentation method. Also, let ${\bf x}_c$ be the component of $\bf x$ formed by elements in clique $c$. The energy function now also contains higher-order potentials 
%
\begin{equation}
    E({\bf x}) = \sum_{a \in {\mathcal X}} \phi_a(x_a) + \sum_{(a, b) \in {\mathcal N}} \phi_{ab}(x_a, x_b) + \sum_{c \in {\mathcal C}} \phi_c({{\bf x}_c}),
    \label{eq:energy_hop_min}
  \end{equation}
%

The energy function also defines a probability distribution $P({\bf x})$ as follows:
\begin{equation}
    P({\bf x}) =
    \begin{cases}
        \frac{1}{\mathcal{Z}} \exp(-E({\bf x})) & \quad \text{if} \enskip {\bf x} \in {\mathcal L}^N,\\
       0  & \quad \text{otherwise}. \\
    \end{cases}
\label{eq:crf_prob_distrib}
\end{equation}
The normalization factor $Z = \sum_{{\bf x} \in {\mathcal L}^N} \exp(-E({\bf x}))$ is known as the {\it partition function}.

@@

\mysection{Review: Variational Inference Using Submodular Extensions}
\label{sec:review}
We now summarise the marginal inference method of Zhang et al. \citep{zhang2015higher} which
uses submodular extensions.

@@

\myparagraph{Submodular Extensions} A submodular extension is defined using
a ground set such that some of its subsets correspond to valid CRF labelings.
To obtain such an extension, we need an encoding scheme which gives the sets corresponding to valid CRF labelings.

@@

\myparagraph{Conditional Gradient Algorithm} The conditional gradient algorithm
(algorithm \ref{algo:fw_inference}) \citep{frank1956algorithm} is a good
candidate for solving problem (\ref{eq:min_upper_bound}) due to two reasons.
First, problem \eqref{eq:min_upper_bound} is convex. Second, as solving an LP over EP(F) is computationally tractable (property \ref{prop:greedy}), the conditional gradient can be found efficiently. The algorithm starts with an initial solution $\bf s_0$ (line \ref{line:initial}). At each iteration, we compute the conditional gradient $\bf s^*$ (line \ref{line:cond_grad}), which minimises the linear approximation $g({\bf s}_k) + \nabla g({\bf s}_k)^T ({\bf s} - {\bf s}_k)$ of the objective function. Finally, $\bf s$ is updated by either (i) fixed step size schedule, as in line \ref{line:step_size} of algorithm \ref{algo:fw_inference}, or (ii) by doing line search ${\bf s}_{k+1} = \min_{0 \leq \gamma \leq 1} g(\gamma {\bf s}^* + (1 - \gamma) {\bf s}_{k})$.

@@

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with accurate extensions for different classes of CRF energy functions? Is it possible to identify optimal extensions which yields the tightest bound?

If we introduce a temperature parameter in $P({\bf x})$ (equation \eqref{eq:crf_prob_distrib}) by using $E({\bf x})/T$ and decrease $T$, the resulting distribution starts to peak more sharply around its mode. As $T \to 0$, marginal estimation becomes the same as MAP inference since the resulting distribution $P^0({\bf x})$ has mass 1 at its mode ${\bf x}^*$ and is 0 everywhere else. Given the MAP solution ${\bf x}^*$, one can compute the marginals as $P(X_i = j) = [x_i^* = j]$, where [.] is the Iverson bracket.

  Motivated by this connection, we ask if one can introduce a temperature parameter to our problem \eqref{eq:min_upper_bound} and transform it to an LP relaxation in the limit $T \to 0$? We can then hope to use accurate LP relaxations of MAP problems known in literature to find good submodular extensions for different classes of energy functions.

@@

In this paper, we focus on submodular extension families $\mathcal F(.)$ corresponding to different classes of energy functions $\mathcal E$. Given an instance of the energy function $E(.)$ from the class $\mathcal E$,  there is a corresponding submodular extension ${\mathcal F}(E)$. Also, we seek a closed-form analytical expression for $\mathcal F$.

@@

Our extensions are derived from LP relaxations. When the LP relaxation is the tightest known, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This implies that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the extension is best for every instance of the energy function. It may be possible to solve an optimisation problem to obtain the best extension for every given instace of energy $E(.)$. However, in this paper, we do not take that approach, and instead provide a general solution for a given class of energy function.

@@

\mysubsection{Pairwise Potts Model}
\label{subsec:potts}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}:
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

\myparagraph{Set Encoding} We choose to use the $1$-of-$L$ encoding for Potts model as described in section \ref{sec:review}. With the encoding scheme for Potts model above, $g({\bf s})$ can be factorised and problem (\ref{eq:min_upper_bound}) can be rewritten as:
%
\begin{equation}
\min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \log \sum_{i = 1}^L \exp(-s_{ai}).
\label{eq:potts_upper_bound}
\end{equation}
(See Remark 1 in appendix)
\myparagraph{Marginal Estimation with Temperature} We now introduce
a temperature parameter $T > 0$ to problem \eqref{eq:potts_upper_bound} which
divides $E({\bf x})$, or equivalently divides $\bf s$ belonging to $EP(F)$. Also, since $T > 0$, we can multiply the objective by $T$ leaving the problem unchanged. Without changing the solution, we can transform problem \eqref{eq:potts_upper_bound} as follows
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad g_T ({\bf s}) = \sum_{a = 1}^{N} T \cdot \log \sum_{i = 1}^L \exp(-\frac{s_{ai}}{T}).
\label{eq:potts_temp}
\end{equation}

@@

The above problem is equivalent to an LP relaxation of the corresponding MAP estimtation problem (see Remark 2 in appendix). We note that $g_T ({\bf s})$ in problem \eqref{eq:potts_temp} becomes the objective function of an LP relaxation in the limit $T \to 0$. We seek to obtain the worst-case optimal submodular extension by making $g_T ({\bf s})$ same as the objective of (P-LP) as $T \to 0$. Since at $T = 1$, problems \eqref{eq:potts_temp} and \eqref{eq:potts_upper_bound} are equivalent, this gives us the worst-case optimal extension for our problem \eqref{eq:potts_upper_bound}.

@@

Potts model imposes the same penalty for unequal assignment of labels to neighbouring variables, regardless of the label dissimilarity. A more natural approach is to vary the penalty based on how different the labels are. A hierarchical Potts model permits this by specifying the distance between labels using a tree with the following properties:
\vspace{2mm}
\begin{enumerate}
  \itemsep+1em 
\item The vertices are of two types: (i) the leaf nodes representing labels, and (ii) the non-leaf nodes, except the root, representing meta-labels.
\item The lengths of all the edges from a parent to its children are the same.
\item The lengths of the edges along any path from the root to a leaf decreases by a factor of at least $r \geq 2$ at each step.
\item The metric distance between nodes of the tree is the sum of the edge lengths on the unique path between them. 
\end{enumerate}
\vspace{2mm}
%
\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/rhst_notation.png}
\mycaption{\footnotesize \em A hierarchical Potts model instance illustrating notations with 2 meta-labels (blue) and 4 labels (yellow). All labels are at the same level. $r = 2$, that is, edge-length decreases by 2 at each level. Also, distance between labels 1 and 3 is $d(1, 3) = 0.5 + 1 + 1 + 0.5 = 3$.} 
\label{fig:rhst}
\end{figure}

A subtree $T$ of an hierarchical Potts model is a tree comprising all the descendants of some node $v$ (not root). Given a subtree $T$, $l_T$ denotes the length of the tree-edge leading upward from the root of $T$ and $L(T)$ denotes the set of leaves of $T$. We call the leaves of the tree as labels and all other nodes of the tree expect the root as \emph{meta-labels}. Figure \ref{fig:rhst} illustrates the notations in the context of a hierarchical Potts model.
%
\myparagraph{Tightest LP Relaxation} We use the same indicator variables $y_{ai}$ that were employed in the LP relaxation of Potts model. Let $y_a(T) = \sum_{i \in L(T)} y_{ai}$. The following LP relaxation is the tightest known for hierarchical Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
\text{(T-LP)} \quad \min_{\bf y} \enskip & \widetilde{E}({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
                                         &\sum_{(a, b) \in {\mathcal N}} w_{ab} \sum_T l_T \cdot |y_{a}(T) - y_{b}(T)| \nonumber\\
    \text{such that} \quad &{\bf y} \in \Delta.
\label{eq:t-lp}
\end{align}
The set $\Delta$ is the same domain as defined in equation (\ref{eq:delta}).

@@

The above problem is equivalent to an LP relaxation of the corresponding MAP
estimtation problem (see Remark 3 in appendix). Hence, $g_T ({\bf s})$ becomes the objective function of an LP relaxation in the limit $T \to 0$. We seek to make this objective same as $\widetilde{E}({\bf z})$ of (T-LP-FULL) in the limit $T \to 0$. The question now becomes how to recover the  worst-case optimal submodular extension from $\widetilde{E}({\bf z})$.
%
{\proposition The  worst-case optimal submodular extension for hierarchical Potts model is given by $F_{hier}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
Also, $\widetilde{E}({\bf z})$ in (T-LP-FULL) is the Lovasz extension of $F_{hier}$.
\label{proposition:rhst_worst-case optimal}}
(Proof in appendix)

@@

Algorithm \ref{algo:fw_inference} assumes that the conditional gradient $\bf s^*$ in step {\ref{line:cond_grad}} can be computed efficiently. This is certainly not the case for dense CRFs, since computing $s^*$ involves $NL$ function evaluations of the submodular extension $F$, where $N$ is the number of variables, and $L$ is the number of labels. Each $F$ evaluation has complexity ${\mathcal O}(N)$ using the efficient Gaussian filtering algorithm of \citep{koltun2011efficient}. However, computation of $s^*$ would still be ${\mathcal O} (N^2)$ this way, which is clearly impractical for computer-vision applications where $N \sim 10^5 - 10^6$.

@@

We now relax the indicator variables $y_{ai}$ to lie in $[0, 1]$. Assuming the pairwise potentials in equation (\ref{eq:energy_hop_min}) to be Potts model, an accurate LP relaxation for the higher-order diversity model is given by:

>>>>

\mysection{Introduction}
The desirable optimization properties of submodular set functions have been
widely exploited in the design of approximate MAP estimation algorithms for
discrete conditional random fields (CRFs) \citep{boykov2001fast,
kumar2011improved}. Submodularity has also been recently used to design an
elegant variational inference algorithm to compute the marginals of a discrete
CRF by minimising an upper-bound on the log-partition function. In the initial
work of \citep{djolonga2014map}, the energy of the CRF was restricted to be
submodular. In a later work ~\citep{zhang2015higher}, the algorithm was
extended to handle more general Potts energy functions. The key idea there was to define a large ground set such that its subsets represent valid labelings, sublabelings or even incorrect labelings (these may assign two separate labels to a random variable and hence be invalid). Given the large ground set, it is possible to define a submodular set function whose value is equal to the energy of the CRF for subsets that specify a valid labeling of the model. We refer to such a set function as a {\em submodular extension} of the energy.

@@

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. Specifically, the Lovasz extension of a submodular extension can be shown to be an objective function for the LP relaxation. This
connection has four important practical consequences. First, it establishes
the optimality of the submodular extension of the Potts model, via the tightest LP relaxation
under UGC-hardness assumptions. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Fourth, we obtain an accurate 
submodular extension for a higher-order diversity model based on an LP
relaxation. Higher-order models can capture interesting properties of the image that cannot be
expressed using pairwise models~\citep{vineet2014filter, kohli2007p3}. We show that our upper-bounds on synthetic problems are comparable to those from tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using pairwise dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. We also perform semantic segmentation on the MSRC-21 dataset using a combination of dense pairwise and higher-order diversity model. The complete code is available at \url{https://github.com/pankajpansari/denseCRF}.

@@

We now introduce the notation and definitions that we make use of in the remainder of the paper.

@@

\myparagraph{Lovasz Extension} For a given set function $F$ with $F(\emptyset) = 0$, the value of its Lovasz extension $f({\bf w}): \mathbb{R}^N \to \mathbb{R}$ is defined as follows: order the components of $\bf w$ in decreasing order such that $w_{j_1} \geq w_{j_2} \geq \dots \geq w_{j_N}$, where $(j_1, j_2, \dots, j_N)$ is the corresponding permutation of the indices. Then,
%
\begin{align}
    f({\bf w}) = \sum_{k = 1}^{N} w_{j_k} \left(F(j_1, \dots, j_k) - F(j_1,
    \dots, j_{k - 1})\right).
    \label{eq:lovasz_def}
\end{align}
%
The function $f$ is an extension because it equals $F$ on the vertices of the
unit cube. That is, for any $A \subseteq V$, $f({\bf 1}_A) = F(A)$, where ${\bf
1}_A$ is the $0\mhyphen{1}$ indicator vector corresponding to the elements of $A$.

@@

We can augment the above pairwise models with higher-order potentials. Let
$\mathcal C$ be the set of cliques on subgroups of variables. These cliques
can, for instance, be the set of superpixels from a clustering method, such as
$k$-means or mean-shift \cite{comaniciu2002mean}. Also, let ${\bf x}_c$ be the component of $\bf x$ formed by elements in clique $c$. The energy function now also contains higher-order potentials 
%
\begin{equation}
    E({\bf x}) = \sum_{a \in {\mathcal X}} \phi_a(x_a) + \sum_{(a, b) \in {\mathcal N}} \phi_{ab}(x_a, x_b) + \sum_{c \in {\mathcal C}} \phi_c({{\bf x}_c}),
    \label{eq:energy_hop_min}
  \end{equation}
%

The energy function can be interpreted as defining a probability distribution $P({\bf x})$ as follows:
\begin{equation}
    P({\bf x}) =
    \begin{cases}
        \frac{1}{\mathcal{Z}} \exp(-E({\bf x})) & \quad \text{if} \enskip {\bf x} \in {\mathcal L}^N,\\
       0  & \quad \text{otherwise}. \\
    \end{cases}
\label{eq:crf_prob_distrib}
\end{equation}
The normalization factor $Z = \sum_{{\bf x} \in {\mathcal L}^N} \exp(-E({\bf x}))$ is known as the {\it partition function}.

@@

\mysection{Review: Variational Inference Using Submodular Extensions}
\label{sec:review}
We now summarise the marginal inference method of Zhang et al. \citep{zhang2015higher} which
made use of a submodular extension.

@@

\myparagraph{Submodular Extensions} A submodular extension is defined using
a ground set such that some of its subsets correspond to valid CRF labelings.
Note that not every subset needs to represent a valid labeling - some of them could
correspond to incomplete or invalid labelings. To obtain such an extension, we need an encoding scheme which gives the sets corresponding to valid CRF labelings.

@@

\myparagraph{Conditional Gradient Algorithm} The conditional gradient algorithm
(algorithm \ref{algo:fw_inference}) \citep{frank1956algorithm} is a good
candidate for solving problem (\ref{eq:min_upper_bound}) due to two reasons.
First, problem \eqref{eq:min_upper_bound} is convex. Second, as solving an LP
over EP(F) is computationally tractable (property \ref{prop:greedy}), the
conditional gradient can be found efficiently. The algorithm starts with an
initial solution $\bf s_0$ (line \ref{line:initial}). At each iteration, we
compute the conditional gradient $\bf s^*$ (line \ref{line:cond_grad}), which
minimises the linear approximation $g({\bf s}_k) + \nabla g({\bf s}_k)^T ({\bf
s} - {\bf s}_k)$ of the objective function. Finally, $\bf s$ is updated by
either (i) fixed step size schedule, as in line \ref{line:step_size} of
algorithm \ref{algo:fw_inference}, or (ii) by doing a line search and setting ${\bf s}_{k+1} = \min_{0 \leq \gamma \leq 1} g(\gamma {\bf s}^* + (1 - \gamma) {\bf s}_{k})$.

@@

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with accurate extensions for different classes of CRF energy functions? Is it possible to identify optimal extensions which yield the tightest bound?

If we introduce a temperature parameter in $P({\bf x})$ (equation
\eqref{eq:crf_prob_distrib}) by using $E({\bf x})/T$ and decrease $T$, the
resulting distribution starts to peak more sharply around its mode. This
is assuming that $P({\bf x})$ is unimodal, and there aren't multiple solutions
with the same minima. As $T \to 0$, marginal estimation becomes the same as MAP inference since the resulting
distribution $P^0({\bf x})$ has mass 1 at its mode ${\bf x}^*$ and is
0 everywhere else. Given the MAP solution ${\bf x}^*$, one can compute the
marginals as $P(X_i = j) = [x_i^* = j]$, where [.] is the Iverson bracket. Motivated by this connection, we ask if one can introduce a temperature parameter to our problem \eqref{eq:min_upper_bound} and transform it to an LP relaxation in the limit $T \to 0$? We can then hope to use accurate LP relaxations of MAP problems known in literature to find good submodular extensions for different classes of energy functions.

@@

In this work, we focus on submodular extension families $\mathcal F(.)$
corresponding to different classes of energy functions $\mathcal E$. Given an
instance of the energy function $E(.)$ from the class $\mathcal E$,  there is
a corresponding submodular extension ${\mathcal F}(E)$. Moreover, we seek a closed-form analytical expression for $\mathcal F$.

@@

Our extensions are derived from LP relaxations. When the LP relaxation is the
tightest possible, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This is to say that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the
extension is best for every instance of the energy function. It may be possible
to solve an optimisation problem to obtain the best extension for every given
instance of energy $E(.)$. However, in this paper, we do not take that approach, and instead provide a general solution for a given class of energy function.

@@

\mysubsection{Pairwise Potts Model}
\label{subsec:potts}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and
submodular extension, we briefly outline the LP relaxation of the corresponding
MAP estimation problem. To this end, we define indicator variables $y_{ai}$
which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the
tightest possible for Potts model in the worst-case, assuming the Unique Games
Conjecture is true \citep{manokaran2008sdp}:
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

\myparagraph{Set Encoding} We choose to use the $1$-of-$L$ encoding for Potts model as described in section \ref{sec:review}. With the encoding scheme for Potts model above, $g({\bf s})$ can be factorised and problem (\ref{eq:min_upper_bound}) can be rewritten as:
%
\begin{equation}
\min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \log \sum_{i = 1}^L \exp(-s_{ai}).
\label{eq:potts_upper_bound}
\end{equation}
(See Remark 1 in appendix A for proof)
\myparagraph{Marginal Estimation with Temperature} We now introduce
a temperature parameter $T > 0$ to problem \eqref{eq:potts_upper_bound} which
divides $E({\bf x})$, or equivalently divides $\bf s$ belonging to $EP(F)$. Also, since $T > 0$, we can multiply the objective by $T$ leaving the problem unchanged. Without changing the solution, we can transform problem \eqref{eq:potts_upper_bound} as follows
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad g_T ({\bf s}) = \sum_{a = 1}^{N} T \cdot \log \sum_{i = 1}^L \exp(-\frac{s_{ai}}{T}).
\label{eq:potts_temp}
\end{equation}

@@

The above problem is equivalent to an LP relaxation of the corresponding MAP
estimation problem (see Remark 2 in appendix). We note that $g_T ({\bf s})$ in
problem \eqref{eq:potts_temp} becomes the objective function of an LP
relaxation in the limit $T \to 0$. We seek to obtain the worst-case optimal
submodular extension by making $g_T ({\bf s})$ same as the objective of (P-LP)
as $T \to 0$. We note that problems \eqref{eq:potts_temp} and
\eqref{eq:potts_upper_bound} become equivalent at $T = 1$, and our worst-case optimality
guarantee was derived in the limit $T \to 0$. However, it is possible to
derive such a guarantee only in the limit case, and it is in this sense that we
claim the worst-case optimality.

@@

Potts model imposes the same penalty for unequal assignment of labels to
neighbouring variables, regardless of the label dissimilarity. In some
scenarios, a more natural approach is to vary the penalty based on how different the labels are. A hierarchical Potts model permits this by specifying the distance between labels using a tree with the following properties:
\vspace{2mm}
\begin{enumerate}
  \itemsep+1em 
\item The vertices are of two types: (i) the leaf nodes representing labels, and (ii) the non-leaf nodes, except the root, representing meta-labels.
\item The lengths of all the edges from a parent to its children are the same.
\item The lengths of the edges along any path from the root to a leaf decreases by a factor of at least $r \geq 2$ at each step.
\item The metric distance between nodes of the tree is the sum of the edge lengths on the unique path between them. 
\end{enumerate}
\vspace{2mm}
%
\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/rhst_notation.png}
\mycaption{\footnotesize \em A hierarchical Potts model instance illustrating notations with 2 meta-labels (blue) and 4 labels (yellow). All labels are at the same level. $r = 2$, that is, edge-length decreases by 2 at each level. Also, distance between labels 1 and 3 is $d(1, 3) = 0.5 + 1 + 1 + 0.5 = 3$.} 
\label{fig:rhst}
\end{figure}

A subtree $T$ of an hierarchical Potts model is a tree comprising all the descendants of some node $v$ (not root). Given a subtree $T$, $l_T$ denotes the length of the tree-edge leading upward from the root of $T$ and $L(T)$ denotes the set of leaves of $T$. We call the leaves of the tree as labels and all other nodes of the tree expect the root as \emph{meta-labels}. Figure \ref{fig:rhst} illustrates the notations in the context of a hierarchical Potts model.
%
\myparagraph{Tightest LP Relaxation} We use the same indicator variables
$y_{ai}$ that were employed in the LP relaxation of Potts model. Let $y_a(T)
= \sum_{i \in L(T)} y_{ai}$. The following LP relaxation is the tightest known
for hierarchical Potts model in the worst-case, assuming the Unique Games
Conjecture is true \citep{manokaran2008sdp}
\begin{align}
\text{(T-LP)} \quad \min_{\bf y} \enskip & \widetilde{E}({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
                                         &\sum_{(a, b) \in {\mathcal N}} w_{ab} \sum_T l_T \cdot |y_{a}(T) - y_{b}(T)| \nonumber\\
    \text{such that} \quad &{\bf y} \in \Delta.
\label{eq:t-lp}
\end{align}
The set $\Delta$ is the same domain as defined in equation (\ref{eq:delta}).

@@

The above problem is equivalent to an LP relaxation of the corresponding MAP
estimation problem (see Remark 3 in appendix). Hence, $g_T ({\bf s})$ becomes the objective function of an LP relaxation in the limit $T \to 0$. We seek to make this objective same as $\widetilde{E}({\bf z})$ of (T-LP-FULL) in the limit $T \to 0$. The question now becomes how to recover the  worst-case optimal submodular extension from $\widetilde{E}({\bf z})$.
%
{\proposition The  worst-case optimal submodular extension for hierarchical Potts model is given by $F_{hier}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
Also, $\widetilde{E}({\bf z})$ in (T-LP-FULL) is the Lovasz extension of $F_{hier}$.
\label{proposition:rhst_worst-case optimal}}
(Proof in appendix)

@@

Algorithm \ref{algo:fw_inference} assumes that the conditional gradient $\bf s^*$ in step {\ref{line:cond_grad}} can be computed efficiently. This is certainly not the case for dense CRFs, since computing $s^*$ involves $NL$ function evaluations of the submodular extension $F$, where $N$ is the number of variables, and $L$ is the number of labels. Each $F$ evaluation has complexity ${\mathcal O}(N)$ using the efficient Gaussian filtering algorithm of \citep{koltun2011efficient}. However, computation of $s^*$ would still be ${\mathcal O} (N^2)$, which is clearly impractical for computer-vision applications where $N \sim 10^5 - 10^6$.

@@

We now relax the indicator variables $y_{ai}$ to lie in $[0, 1]$. Assuming the pairwise potentials in equation (\ref{eq:energy_hop_min}) to be Potts, an accurate LP relaxation for the higher-order diversity model is given by:
